---
title: "P3 Assessment - Solution"
author: "WXXXX KXXX AXXXXXXX"
date: "2024-08-17"
output: html_document
---

```{r setup, include=FALSE}

# General options for code chunks
knitr::opts_chunk$set(echo = FALSE, 
                      comment = "",
                      warning = FALSE,
                      message = FALSE)
```

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}

## function to install and load multiple R packages.
## check to see if packages are installed. Install them if they are not, then load them into the R session

install <- function(pkg){
  # check the provided list of packages if they are installed or not
  # extract only those which are not installed
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    # in case there were packages which were not installed yet, they will be installed
    # from provided repository
    install.packages(new.pkg, dependencies = TRUE, repos = "http://cran.us.r-project.org")
  # load all the packages to the R Env
  sapply(pkg, require, character.only = TRUE)
}

```

## Task1 - Solution
In task one, although all the data-sets were already existed in the `01_rawdata`, and the [LINK](https://data.unicef.org/resources/data_explorer/unicef_f/?ag=UNICEF&df=GLOBAL_DATAFLOW&ver=1.0&dq=.MNCH_ANC4+MNCH_SAB.&startPeriod=2018&endPeriod=2022) was also provided for the external data-set. Normally the data can be pulled from webpages and URLs with simple `R Script` or HTTP requests. However, in this case I browsed the URL in a browser and downloaded the data in an Excel file (from the download option on the page) and I also added the Excel file in the `01_rawdata` folder. The reason was that reading data from a URL which loads data dynamically using JavaScript/AJAX, that needed some advanced techniques and some libraries that needed to be compiled locally e.g., `RSelenium` and some others, and I thought that might not be needed for this exercise. In a real word, this data can be extracted from the Indicator Data Warehouse (SDMX). 

```{r common_packages, warning=FALSE, message=FALSE, echo=FALSE}
# Load the common packages for this exercise - in invisible mode
invisible(install(c("readxl", "tidyverse", "lubridate")))

```

### Step1: 
Load, clean and transform the Data downloaded from the DATA.UNICEF.ORG Website (Provided URL) <br>
Here's a sample of the data:

```{r load_wh_data, echo=FALSE}

# Load Data Downloaded from OPEN.DATA.UNICEF, Clean and Transform it a little bit
# Skipping the first 2 rows, those are the merged column headers, we don't need them here
anc_sub_data <- read_excel(path = "01_rawdata/GLOBAL_DATAFLOW_2018-2022.xlsx", skip = 2) %>% suppressMessages()

# Assign new column names to the data-set
colnames(anc_sub_data) <- c("Country", "Indicator", "Gender", "2022", "2021", "2020", "2019", "2018")

# Make some cleaning and transformation
anc_sub_data <- anc_sub_data %>% 
  filter(!is.na(Indicator)) %>% # remove the extra rows at the end of the data-set in Excel
  # Replace - with NA in all data columns/rows
  mutate(across(all_of(c("2022", "2021", "2020", "2019", "2018")), ~ na_if(., "-"))) %>%
  # Add a new column and put the value of latest year there (non-NA value). 
  mutate(Latest_Value = coalesce(`2022`, `2021`, `2020`, `2019`, `2018`))

# Show a sample of the data
# let's make the table a bit nicer and show only 5 rows
knitr::kable(head(anc_sub_data, n = 5))

```

### Step 2:
Load the SDG Status Analysis of Under5 Mortality Target by Countries, clean and transform as needed and merge it with the `ANC & SUB Indicators Data`, prepared above. <br>
Here's a sample of the loaded data:

```{r load_sdg_on_off_data, echo=FALSE}
# Load On-Off-Track Data
on_off_track_sdgs <- read_excel(path = "01_rawdata/On-track and off-track countries.xlsx") %>% suppressMessages()

# Print a sample of the data
knitr::kable(head(on_off_track_sdgs))

```

Below is a sample of the merged data:
```{r merge_data, echo=FALSE}

# Now merging the two data-sets, will need left join, because in our indicators data set we have extra locations' categories (Africa, America, etc. etc.), Which we don't have in the ON-OFF Track SDGs data, which is only by Country - so everything from the first data-set will be included and matched ones from the second data-set. 
merged_dataset <- left_join(anc_sub_data, on_off_track_sdgs, by = c("Country" = "OfficialName"))

# only 5 rows
knitr::kable(head(merged_dataset, n=5))

```

### Step 3: 
Load the Demographic Data - which has the Birth Rate Projection, there are two sheets in that Excel Workbook, the Projections sheet will be loaded as it has the Birth Rate Projection. 
Some transformation and filtering (to filter only 2022 projection) is also performed and it is merged with the data prepared above. In this step a sample of data is not shown because the data-set have many columns. 

```{r load_projection_data, echo=FALSE}

# Skipping 16 first rows, that's not the data, there are some merged cells and titles
# also setting the guess_max parameters, so R can guess the column type properly. 
birth_rate_projection <- read_excel(path = "01_rawdata/WPP2022_GEN_F01_DEMOGRAPHIC_INDICATORS_COMPACT_REV1.xlsx", guess_max = 5000, sheet = "Projections", skip = 16) %>% suppressMessages()

# remove other years projection, keep only 2022
birth_rate_projection <- birth_rate_projection %>% 
  filter(Year == 2022)

# rename column 3
names(birth_rate_projection)[3] <- "Region_SubRegion_Country_Area"

# head(birth_rate_projection)
# merge with data prepared above - again it will be a left_join
merged_dataset <- left_join(merged_dataset, birth_rate_projection, by = c("Country" = "Region_SubRegion_Country_Area"))

```

### Final Step:
As the data is ready, in this step Weighted Coverage will be calculated as per the provided formula.  The `group_by` and `summarise` functions were used for this purpose, including SUM, Multiplication and Division. As instructed,only the calculation for Countries is needed, therefore the other type of locations are filtered out, also the data has been prepared for the calculation (e.g., changing the datatypes of the columns, etc.). The long indicators names were also replaced by shorter names, to look better on the visualization/chart. 

```{r weighted_coverage, echo=FALSE}

wc_calc <- merged_dataset %>%
  # only keep the Countries
  filter(!is.na(ISO3Code)) %>%
  # change the datatype to numeric (the data is in thousands, we will keep as is even if we multiply by 1000, the final result of the formula will not change)
  mutate(`Births (thousands)` = as.numeric(`Births (thousands)`)) %>%
  mutate(Latest_Value = as.numeric(Latest_Value)) %>%
  # Keep only two categories (On/Off Track)
  mutate(SDG_Status_U5MR = ifelse(
    Status.U5MR == "Achieved" | Status.U5MR == "On Track", "On Track", "Off Track"
  )) %>%
  # replace the long text to shorter text - indicators
  mutate(Indicator = case_when(
    str_detect(Indicator, "^Antenatal care 4") ~ "Antenatal care 4+ visits (ANC4)",
    str_detect(Indicator, "^Skilled birth attendant") ~ "Skilled birth attendant (SAB)",
    TRUE ~ Indicator
  )) %>%
  # We need the result to be by Indicator and by SDG Status - Group by them
  group_by(Indicator, SDG_Status_U5MR) %>%
  summarise(
    # Sum of Countries Coverage * Birth Rate Projection / Sum of Birth Rate Projection - Keep NA Removed
    Weighted_Coverage = sum(Latest_Value * `Births (thousands)`, na.rm = TRUE) / sum(`Births (thousands)`, na.rm = TRUE)
  ) %>%
  ungroup()

#print(wc_calc)

```
Here's the result for the Weighted Coverage for both indicators by SDG U5MR Status:
```{r print_wc}
knitr::kable(wc_calc)
```

As now the data is ready visualization, I will simply plot it. I used Bar-Chart for this purpose - which is the best for comparing data side by side (On/Off countries). 

Here's the required visualization (Bar Chart)

```{r bar_chart_weighted_coverage, fig.width= 8, fig.height= 5, message = FALSE, results='asis'}
# GGPLOT2 is used - X Axis will show Indicator - Y will show Weighted Coverage filled by different colors of On/Off
# First let's reorder the Data-Set so we can plot the on/off track correctly
wc_calc$SDG_Status_U5MR <- factor(wc_calc$SDG_Status_U5MR, levels = c("On Track", "Off Track"))
ggplot(wc_calc, aes(x = Indicator, y = Weighted_Coverage, fill = SDG_Status_U5MR)) +
  labs(title = "Weighted Coverage of Countries by Indicator and SDG Status of U5 Mortality Rate Target", 
       x = "Indicator",
       y = "Weighted Coverage",
       fill = "SDG Status U5MR") +
  # make it a bar type - use the actual values of the Y axis (Weighted_Coverage) and place it side by side
  geom_bar(stat = "identity", position = "dodge") +
  # add data labels - round the values to 1 decimal point
  geom_text(aes(label = round(Weighted_Coverage, 1)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) + 
  # Manually set the colors for the bars
  scale_fill_manual(
    values = c("On Track" = "#09a3cd", "Off Track" = "#e45b5b"),
    breaks = c("On Track", "Off Track")  # Order the legend
  ) +
  theme_classic() +
  # place the legend on the top
  theme(legend.position = "top")

```

## Task 2 - Solution (Data Perspective)
As required for this task, the MICS Survey data is loaded, transformed and evaluated. As a first step, the data has been loaded, making sure that all variables (columns) in the data-set has correct data-types, and then some basic summary analysis of the data-set has been performed, before analyzing the key aspects (areas) as requested. 

```{r load_zim_mics_data}

# vector to store questions labels and codebook, can be used later

questions <- c(
  EC6 = "Can (name) identify or name at least ten letters of the alphabet?", 
  EC7 = "Can (name) read at least four simple, popular words?",
  EC8 = "Does (name) know the name and recognize the symbol of all numbers from 1 to 10?",
  EC9 = "Can (name) pick up a small object with two fingers, like a stick or a rock from the ground?",
  EC10 = "Is (name) sometimes too sick to play?", 
  EC11 = "Does (name) follow simple directions on how to do something correctly?", 
  EC12 = "When given something to do, is (name) able to do it independently?", 
  EC13 = "Does (name) get along well with other children?", 
  EC14 = "Does (name) kick, bite, or hit other children or adults?", 
  EC15 = "Does (name) get distracted easily?"
)
# Load the data
zim_mics_data <- read.csv("01_rawdata/Zimbabwe_children_under5_interview.csv")

summary(zim_mics_data)

```

From the Summary Analysis above, it's clear that some variables data types are incorrect (interview_data, child_birthday), since one of the requirement of this task is to analyze the areas of interest in consideration of time (time series analysis) and for that it's needed to keep the data in the correct format. Secondly, the categories will also be replaced with their textual representation, so the data can be more readable. 
A new variable is added to the data-set (month) in `2018-12` format, that's extracted from the interview data. For this analysis, it's assumed that repeated interviews were taken in the same locations in different months, to observe children growth.  

```{r zim_mics_data_transform}

# Convert the character string to a date format
zim_mics_data$interview_date <- as.Date(zim_mics_data$interview_date, format = "%Y-%m-%d")
zim_mics_data$child_birthday <- as.Date(zim_mics_data$child_birthday, format = "%Y-%m-%d")

# Extract the month from the interview_date
zim_mics_data$month <- format(zim_mics_data$interview_date, "%Y-%m")

# Convert categorical variables to factors with labels
categorical_vars <- c("EC6", "EC7", "EC8", "EC9", "EC10", "EC11", "EC12", "EC13", "EC14", "EC15")

# replace the categorical variables with the respective labels. 
zim_mics_data[categorical_vars] <- lapply(zim_mics_data[categorical_vars], factor, levels = c(1, 2, 8), labels = c("Yes", "No", "DK"))

# print a sample of the transformed data
knitr::kable(head(zim_mics_data, n=5))

```

### Methodology

For the analysis of the data, a form of time-series analysis method is used, because the indicators (children growth in specified areas) need to be looked up month by month. As mentioned above, the interview date will be considered as a date variable (in our case month) and based on that the other variables (indicators) will be analyzed. Trend charts (stacked bar) are created for the specified educational areas, and the responses (categories of responses) will be used to evaluate the distribution of response (by category) in each month. Proportion for each category of the responses are highlighted. 

### Learning and Simple Math Skills:
EC6: Can (name) identify or name at least ten letters of the alphabet? <br>
EC7: Can (name) read at least four simple, popular words? <br>
EC8: Does (name) know the name and recognize the symbol of all numbers from 1 to 10? <br>

```{r learning_math, fig.width= 9, fig.height= 4, message = FALSE, results='asis'}
# Prepare the data
literacy_math <- zim_mics_data %>%
  # only select the 3 related vars and month columns
  select(month, EC6, EC7, EC8) %>%
  # change the data to longer format
  pivot_longer(cols = c(EC6, EC7, EC8), names_to = "question", values_to = "response") %>%
  # group by and summarise (count) the responses categories and then ungroup
  group_by(month, question, response) %>%
  # summarize and add a count to the dataframe
  summarise(count = n(), .groups = 'drop') %>%
  # another group by to find total responses in each month for the propotion calculation 
  group_by(month, question) %>%
  # add columns to show the proportion (by each category) and total (by month/question)
  mutate(proportion = count / sum(count),
         total = sum(count)) %>%
  ungroup()

# replace the coded questions to the real-text
literacy_math <- literacy_math %>% 
  rowwise() %>%
  mutate(question = ifelse(question == "EC6", questions["EC6"],
                                ifelse(question == "EC7", questions["EC7"],
                                       ifelse(question == "EC8", questions["EC8"], question))))

# Reorder the levels of response for correct stacking and legend order, 
# which will display as (Yes, No, DK and NA)
literacy_math$response <- factor(literacy_math$response, levels = c("NA", "DK", "No", "Yes"))
# Sort the data to enforce the stacking order
literacy_math <- literacy_math %>%
  arrange(month, question, response)


# Plot the data, fill by response and group the stack by response categories as well
ggplot(literacy_math, aes(x = month, y = proportion, fill = response, group = response)) +
  # bar chart - stat is the identity which will take the proportion value
  # fill will make sure to reach to 100% and then each group will stack on top of each
  # other which will represent the proportion of each category
  geom_bar(stat = "identity", position = "fill") +
  
  # now we have 3 questions, let's create multiple plots by providing the question param to below 
  # facet_wrap function with ~ also show the questions text on top of the chart - wrap it if longer than 40 chars
  facet_wrap(~question, labeller = labeller(question = function(x) str_wrap(x, width = 40))) +
  
  # Set the titles (title/axis labels)
  labs(title = "Trends of Learning and Simple Math Skills during the months of Interview",
       x = "Year - Month",
       y = "Proportion of Responses",
       fill = "Response") +
  # manually specify the colors to each category
  scale_fill_manual(
    values = c("NA" = "grey", "DK" = "#fbc449", "No" = "#e45b5b", "Yes" = "#09a3cd" ),
    breaks = c("Yes", "No", "DK", "NA")  # Order the legend as Yes, No, DK, NA
  ) +
  theme_minimal() +
  theme(legend.position = "top", plot.title = element_text(hjust = 0.5)) +
  
  # Add total count at the top of each bar
  geom_text(aes(label = total, y = 1.05), 
            vjust = 0, size = 3, color = "black") +
  
  # Add category-specific counts inside each section
  geom_text(aes(label = count), 
            position = position_stack(vjust = 0.5), size = 3, color = "white")



```

### Physical:
EC9: Can (name) pick up a small object with two fingers, like a stick or a rock from the ground? <br>
EC10: Is (name) sometimes too sick to play? <br>

```{r physical, fig.width= 9, fig.height= 4, message = FALSE, results='asis'}

# Prepare the data
physical <- zim_mics_data %>%
  # only select the 2 related vars and month columns
  select(month, EC9, EC10) %>%
  # change the data to longer format
  pivot_longer(cols = c(EC9, EC10), names_to = "question", values_to = "response") %>%
  # group by and summarise (count) the responses categories and then ungroup
  group_by(month, question, response) %>%
  # summarize and add a count to the dataframe
  summarise(count = n(), .groups = 'drop') %>%
  # another group by to find total responses in each month for the propotion calculation 
  group_by(month, question) %>%
  # add columns to show the proportion (by each category) and total (by month/question)
  mutate(proportion = count / sum(count),
         total = sum(count)) %>%
  ungroup()

# replace the coded questions to the real-text
physical <- physical %>% 
  rowwise() %>%
  mutate(question = ifelse(question == "EC9", questions["EC9"],
                                ifelse(question == "EC10", questions["EC10"],
                                        question)))

# Reorder the levels of response for correct stacking and legend order, 
# which will display as (Yes, No, DK and NA)
physical$response <- factor(physical$response, levels = c("NA", "DK", "No", "Yes"))
# Sort the data to enforce the stacking order
physical <- physical %>%
  arrange(month, question, response)


# Plot the data, fill by response and group the stack by response categories as well
ggplot(physical, aes(x = month, y = proportion, fill = response, group = response)) +
  # bar chart - stat is the identity which will take the proportion value
  # fill will make sure to reach to 100% and then each group will stack on top of each
  # other which will represent the proportion of each category
  geom_bar(stat = "identity", position = "fill") +
  
  # now we have 3 questions, let's create multiple plots by providing the question param to below 
  # facet_wrap function with ~ also show the questions text on top of the chart - wrap it if longer than 60 chars
  facet_wrap(~question, labeller = labeller(question = function(x) str_wrap(x, width = 50))) +
  
  # Set the titles (title/axis labels)
  labs(title = "Trends of Physical Skills during the months of Interview",
       x = "Year - Month",
       y = "Proportion of Responses",
       fill = "Response") +
  # manually specify the colors to each category
  scale_fill_manual(
    values = c("NA" = "grey", "DK" = "#fbc449", "No" = "#e45b5b", "Yes" = "#09a3cd" ),
    breaks = c("Yes", "No", "DK", "NA")  # Order the legend as Yes, No, DK, NA
  ) +
  theme_minimal() +
  theme(legend.position = "top", plot.title = element_text(hjust = 0.5)) +
  
  # Add total count at the top of each bar
  geom_text(aes(label = total, y = 1.05), 
            vjust = 0, size = 3, color = "black") +
  
  # Add category-specific counts inside each section
  geom_text(aes(label = count), 
            position = position_stack(vjust = 0.5), size = 3, color = "white")


```

### Learning:
EC11: Does (name) follow simple directions on how to do something correctly? <br>
EC12: When given something to do, is (name) able to do it independently? <br>

```{r learning, fig.width= 9, fig.height= 4, message = FALSE, results='asis'}

# Prepare the data
learning <- zim_mics_data %>%
  # only select the 2 related vars and month columns
  select(month, EC11, EC12) %>%
  # change the data to longer format
  pivot_longer(cols = c(EC11, EC12), names_to = "question", values_to = "response") %>%
  # group by and summarise (count) the responses categories and then ungroup
  group_by(month, question, response) %>%
  # summarize and add a count to the dataframe
  summarise(count = n(), .groups = 'drop') %>%
  # another group by to find total responses in each month for the propotion calculation 
  group_by(month, question) %>%
  # add columns to show the proportion (by each category) and total (by month/question)
  mutate(proportion = count / sum(count),
         total = sum(count)) %>%
  ungroup()

# replace the coded questions to the real-text
learning <- learning %>% 
  rowwise() %>%
  mutate(question = ifelse(question == "EC11", questions["EC11"],
                                ifelse(question == "EC12", questions["EC12"],
                                        question)))

# Reorder the levels of response for correct stacking and legend order, 
# which will display as (Yes, No, DK and NA)
learning$response <- factor(learning$response, levels = c("NA", "DK", "No", "Yes"))
# Sort the data to enforce the stacking order
learning <- learning %>%
  arrange(month, question, response)


# Plot the data, fill by response and group the stack by response categories as well
ggplot(learning, aes(x = month, y = proportion, fill = response, group = response)) +
  # bar chart - stat is the identity which will take the proportion value
  # fill will make sure to reach to 100% and then each group will stack on top of each
  # other which will represent the proportion of each category
  geom_bar(stat = "identity", position = "fill") +
  
  # now we have 3 questions, let's create multiple plots by providing the question param to below 
  # facet_wrap function with ~ also show the questions text on top of the chart - wrap it if longer than 60 chars
  facet_wrap(~question, labeller = labeller(question = function(x) str_wrap(x, width = 50))) +
  
  # Set the titles (title/axis labels)
  labs(title = "Trends of Learning Skills during the months of Interview",
       x = "Year - Month",
       y = "Proportion of Responses",
       fill = "Response") +
  # manually specify the colors to each category
  scale_fill_manual(
    values = c("NA" = "grey", "DK" = "#fbc449", "No" = "#e45b5b", "Yes" = "#09a3cd" ),
    breaks = c("Yes", "No", "DK", "NA")  # Order the legend as Yes, No, DK, NA
  ) +
  theme_minimal() +
  theme(legend.position = "top", plot.title = element_text(hjust = 0.5)) +
  
  # Add total count at the top of each bar
  geom_text(aes(label = total, y = 1.05), 
            vjust = 0, size = 3, color = "black") +
  
  # Add category-specific counts inside each section
  geom_text(aes(label = count), 
            position = position_stack(vjust = 0.5), size = 3, color = "white")
```

### Socio-emotional:
EC13: Does (name) get along well with other children? <br>
EC14: Does (name) kick, bite, or hit other children or adults? <br>
EC15: Does (name) get distracted easily? <br>

```{r socio_emotional, fig.width= 9, fig.height= 4, message = FALSE, results='asis'}
# Prepare the data
socio_emotional <- zim_mics_data %>%
  # only select the 3 related vars and month columns
  select(month, EC13, EC14, EC15) %>%
  # change the data to longer format
  pivot_longer(cols = c(EC13, EC14, EC15), names_to = "question", values_to = "response") %>%
  # group by and summarise (count) the responses categories and then ungroup
  group_by(month, question, response) %>%
  # summarize and add a count to the dataframe
  summarise(count = n(), .groups = 'drop') %>%
  # another group by to find total responses in each month for the propotion calculation 
  group_by(month, question) %>%
  # add columns to show the proportion (by each category) and total (by month/question)
  mutate(proportion = count / sum(count),
         total = sum(count)) %>%
  ungroup()

# replace the coded questions to the real-text
socio_emotional <- socio_emotional %>% 
  rowwise() %>%
  mutate(question = ifelse(question == "EC13", questions["EC13"],
                                ifelse(question == "EC14", questions["EC14"],
                                       ifelse(question == "EC15", questions["EC15"], question))))

# Reorder the levels of response for correct stacking and legend order, 
# which will display as (Yes, No, DK and NA)
socio_emotional$response <- factor(socio_emotional$response, levels = c("NA", "DK", "No", "Yes"))
# Sort the data to enforce the stacking order
socio_emotional <- socio_emotional %>%
  arrange(month, question, response)


# Plot the data, fill by response and group the stack by response categories as well
ggplot(socio_emotional, aes(x = month, y = proportion, fill = response, group = response)) +
  # bar chart - stat is the identity which will take the proportion value
  # fill will make sure to reach to 100% and then each group will stack on top of each
  # other which will represent the proportion of each category
  geom_bar(stat = "identity", position = "fill") +
  
  # now we have 3 questions, let's create multiple plots by providing the question param to below 
  # facet_wrap function with ~ also show the questions text on top of the chart - wrap it if longer than 40 chars
  facet_wrap(~question, labeller = labeller(question = function(x) str_wrap(x, width = 40))) +
  
  # Set the titles (title/axis labels)
  labs(title = "Trends of Socio-Emotional Skills during the months of Interview",
       x = "Year - Month",
       y = "Proportion of Responses",
       fill = "Response") +
  # manually specify the colors to each category
  scale_fill_manual(
    values = c("NA" = "grey", "DK" = "#fbc449", "No" = "#e45b5b", "Yes" = "#09a3cd" ),
    breaks = c("Yes", "No", "DK", "NA")  # Order the legend as Yes, No, DK, NA
  ) +
  theme_minimal() +
  theme(legend.position = "top", plot.title = element_text(hjust = 0.5)) +
  
  # Add total count at the top of each bar
  geom_text(aes(label = total, y = 1.05), 
            vjust = 0, size = 3, color = "black") +
  
  # Add category-specific counts inside each section
  geom_text(aes(label = count), 
            position = position_stack(vjust = 0.5), size = 3, color = "white")



```

### Key Findings
The trends analysis shows the regular progress children make in literacy, math, physical, learning and socio-emotional skills between the ages of 3 and 4. However, some physical (health related indicators) shows variability, which could be because of seasonal sickness, but that need attention both from parents and teachers side in school. Some key findings are listed below:

* **Literacy and Math**: The analysis shows children's ability to recognize letters, words, and numbers improves month by month.

* **Physical**: Trends of Physical Skills improvement shows some variability, that could be because of the seasonal factors (seasonal sickness), but that still need some attention

* **Learning**: The Learning Skills analysis indicates that there's an improvement over time, it tells us that children are gaining confidence and cognitive abilities as they grow.

* **Socio-emotional**: These Skills are also improved over time as the data shows, however, the tendency to get distracted remains high.

<br>
<br>

**Thank You**



